---
title: "국제학교 주요 홍보 동영상 모음"
---

```{r global_options, include=FALSE}
library(knitr)
library(dplyr)

opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE)

wd = c("/Users/Sungpil/GIT/InternationalSchool", "D:/GIT/InternationalSchool", "/Users/Sungpil/GIT/InternationalSchool")
setwd(wd[3])
```

```{r}
# 853x480 # 640x360
WIDTH = 640
HEIGHT = 360

Youtube = function(URL){
  paste0('<br><iframe width=',WIDTH,' height=',HEIGHT,' src="https://www.youtube.com/embed/', URL, '" frameborder="0" allowfullscreen></iframe>')
} 

Vimeo = function(URL){
  paste0('<br><iframe src="https://player.vimeo.com/video/', URL, '" width=',WIDTH,' height=',HEIGHT,' frameborder="0" webkitallowfullscreen mozallowfullscreen allowfullscreen></iframe>')
}
```

# 국제학교 

## CI
1. The Chadwick Way in Songdo, South Korea
`r Youtube("zBeUmAeEeZE")`

1. Chadwick International - school promotion video "Through their eyes" 
`r Youtube("zDzhQHFKbqM")`

## DIS
[Official Youtube](https://www.youtube.com/channel/UCKTaTJz_KW_AWJeER5wK0mA/featured)

1. Welcome to Daegu International School
`r Youtube("C4OHPtEa0KY")`

1. Jet Stream Special Report: The 2015-2016 Yearbook
`r Youtube("4j6lK0kbVys")`

1. Senior Chat (Class of 2016: The Never Ending Story)
`r Youtube("ZlJpTRdcCYk")`

## Branksome Hall Asia
[Official Livestream](http://livestream.com/branksomehallasia)

## NLCS Jeju
1. NLCS JEJU PROMOTIONAL VIDEO ¨START HERE, GO ANYWHERE¨ 
`r Youtube("bzAUVyu-wKM")`

1. 여러분의 인생은 이곳 NLCS JEJU에서 시작됩니다. 우리 학교 출신인 여러분은 진정 어디든 갈 수 있습니다 
`r Youtube("ZdNDWIMu3FA")`

1. Principal for a day
`r Youtube("lnbvxm1-FYo")`

1. Real Madrid Foundation Campus Experience at NLCS Jeju
`r Youtube("xY8qM3DkWOY")`


## KIS Jeju
1. Welcome to the Dorms : Parents Weekend Edition
`r Youtube("W4Yx0rJFqJI")`

1. Korea International School Video Yearbook 2015-2016 
`r Youtube("tB-ck7M3yWo")`

1. Korea International School Video Yearbook 2014-2015
`r Youtube("Q780c-8Vcsg")`

# 외국인학교

## SFS
1. About Seoul Foreign School
`r Youtube("DFFki-XHso0")`

## SIS
1. Why you should choose SIS
`r Youtube("kg8QLZsPGsQ")`

## YISS
1. YISS promotional video (extended version) 
`r Youtube("E8DTctLyoU8")`

# 그외
1. 조기유학! 이제는 제주로~~~
`r Youtube("ITI6UYm7kX4")`


```{r, include=FALSE, eval=FALSE}
`r Youtube("")`
`r Vimeo("")`
```
