---
title: "NeedSchool Video"
author: "PhilDoc"
---

```{r global_options, include=FALSE}
# 무조건 실행하세요!
library(knitr)
library(dplyr)

opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE)
wd = c("/Users/Sungpil/GIT/InternationalSchool", "D:/GIT/InternationalSchool", "/Users/Sungpil/GIT/InternationalSchool")
setwd(wd[3])
```

```{r}
URL = "4j6lK0kbVys"

# 853x480 # 640x360

Youtube = function(URL){
  paste0('<br><iframe width="640" height="360" src="https://www.youtube.com/embed/', URL, '" frameborder="0" allowfullscreen></iframe>')
} 

Vimeo = function(URL){
  paste0('<br><iframe src="https://player.vimeo.com/video/', URL, '" width="640" height="360" frameborder="0" webkitallowfullscreen mozallowfullscreen allowfullscreen></iframe>')
}
```

## SIS


## YISS
1. YISS Introduction
`r Vimeo("36381862")`

## CI 
1. The Chadwick Way in Songdo, South Korea
`r Youtube("zBeUmAeEeZE")`

1. Chadwick International - school promotion video "Through their eyes" 
`r # Youtube("zDzhQHFKbqM")``r Vimeo("135307757")`

## DIS 

[Official Youtube Channel](https://www.youtube.com/channel/UCKTaTJz_KW_AWJeER5wK0mA/featured)

1. Welcome to Daegu International School
`r Youtube("C4OHPtEa0KY")`

1. Jet Stream Special Report: The 2015-2016 Yearbook
`r Youtube("4j6lK0kbVys")`

1. Senior Chat (Class of 2016: The Never Ending Story)
`r Youtube("ZlJpTRdcCYk")`

